Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2018-11-27 scagnostics.Rmd
Comment on holes normalisation added.

Figure \ref{fig:plotV1V2toV3V4} shows the traces representing the index values calculated across a tour between a pair of nuisance projections. The range of each axis is set to be the limits of the index, as might be expected over many different data sets, 0 to 1. Each projection in the interpolation will also be noise. Two different sample sizes are show, $n=100$ as a dashed line, and $n=1000$ as a solid line. The ideal trace is a smooth function, with relatively low values, and no difference between the sample sizes. A major feature to notice is that the scagnostics produce noisy functions, which is problematic, because small changes in the projection result in big jumps in the value. This will make them difficult to optimize. TIC also is noisy. \textcolor{red}{why is TIC so high? did it get inverted?} On the other hand holes, dcor2d, splines2d and MIC are relatively smooth functions. \textcolor{red}{why is holes so high? it should range between 0-1, maybe needs to be better standardised, too.} Several of the indexes are sensitive to sample size also, the same structured projection with differing numbers of points, produces different values.

>>>>

Figure \ref{fig:plotV1V2toV3V4} shows the traces representing the index values calculated across a tour between a pair of nuisance projections. The range of each axis is set to be the limits of the index, as might be expected over many different data sets, 0 to 1. Each projection in the interpolation will also be noise. Two different sample sizes are show, $n=100$ as a dashed line, and $n=1000$ as a solid line. The ideal trace is a smooth function, with relatively low values, and no difference between the sample sizes. A major feature to notice is that the scagnostics produce noisy functions, which is problematic, because small changes in the projection result in big jumps in the value. This will make them difficult to optimize. TIC also is noisy. On the other hand holes, dcor2d, splines2d and MIC are relatively smooth functions. \textcolor{red}{why is holes so high? it should range between 0-1, maybe needs to be better standardised, too.}
\textcolor{blue}{Holes and cmass indexes are derived from $I_0^N$ of \cite{CBC93}. As noted in proposition 1 of that paper the index takes local maxima for the minimum and maximum of $a_0$ which are achieved by central hole and central mass distributions respectively. Ref \cite{Cook:2007:IDG:1557227} then gives explicit index functions defined for sphered data (zero mean, identity variance-covariance matrix). They are defined such that each one is maximised for central holes or central mass type distributions, with maximum=1, and cmass=1-holes. It follows that for either index both large and small values signal deviation from the normal distribution, and given a normal distribution we expect to find "average" index values rather than values close to zero.}
Several of the indexes are sensitive to sample size also, the same structured projection with differing numbers of points, produces different values.
